Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-16 paper/sheaf_lics.tex
reorganize a bit section 5

\item
$\modal \one =\one $
\item
Stability under dependent product (7.7.2 of \cite{hottbook})
\item
 In particular, if $X:\Type_p$ verifies
$P(X)$, then for any $x,y:X$, $P(x=y)$.
\item
Another useful property is that we can extend property {\it (iii)} to
dependent product.
\end{itemize}
\end{prop}

@@

\nt{Il faut introduire c'est propriété, $\Type_n^\modal$ is a sheaf
  est très importante en particulier. Il faut qu'on comprenne d'où ça
  vient et que tu fasses une preuve, même un peu idalisée. Je dirais
  que tu peux mettre des lemmes genres nj\_inter en disant que telle
  flèche est un iso, and co.
  En tout cas, cette partie peut et doit être bien plus longue.
}

@@

\begin{proof}
  As $\mu_T$ is an surjection, we know by Giraud axiom that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.

@@

@@

@@

Prove that the Giraud axiom holds in homotopy type theory.

>>>>

\item
$\modal \one =\one $
\item
Stability under product and dependent product (7.7.2 of \cite{hottbook})
\item
 In particular, if $X:\Type_p$ verifies
$P(X)$, then for any $x,y:X$, $P(x=y)$.
\item
Another useful property is that we can extend property {\it (iii)} to
dependent product.
\end{itemize}
\end{prop}

@@

\nt{Il faut mieux introduire ces propriétés, $\Type_n^\modal$ is a sheaf
  est très importante en particulier. Il faut qu'on comprenne d'où ça
  vient et que tu fasses une preuve, même un peu idalisée. Je dirais
  que tu peux mettre des lemmes genres nj\_inter en disant que telle
  flèche est un iso, and co.
  En tout cas, cette partie peut et doit être bien plus longue.
}

@@

\begin{proof}
  As $\mu_T$ is an surjection, using the particular case of the last
  Giraud-Rezk-Lurie axiom introduced in Section~\ref{sec:giraud-ax},
  we know that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.

@@

\nt{put the definition of $\modal_{n+1}$ upfront}

@@

\nt{Recap what has been done, and give the final result about EM with
  the dense topology as a corollary.}

@@

Prove that the Giraud-Rezk-Lurie axiom holds in homotopy type theory,
or at least the particular case we need.
